\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{0.24\textwidth}>{\raggedright\arraybackslash}X}
\toprule
Component & Configuration \\
\midrule
Input to both models & Fold-selected handcrafted feature vector from the current \texttt{inner-k} setting. Patient-level predictions were computed by averaging held-out window probabilities within each participant. \\
SVM baseline & Linear-kernel SVM with \texttt{C=1.0} and probability estimates enabled. When SMOTE was active in the training folds, class weighting was disabled to avoid double balancing. \\
Hybrid input embedding & Linear projection from the selected feature vector to 128 latent units, followed by normalization, a nonlinear activation, dropout 0.1, and remapping to a learned one-dimensional sequence of length 64. \\
CNN trunk & Three 1D convolutional blocks with filter progressions \texttt{[64,64]}, \texttt{[128,128]}, and \texttt{[256,128]}; kernel sizes \texttt{[5,3]}, \texttt{[3,3]}, and \texttt{[3,1]}; max-pooling factors 2, 2, and 1; batch normalization; and dropout \texttt{[0.1, 0.2, 0.3]}. \\
Recurrent stage & Two bidirectional LSTM layers with 128 and 64 hidden units followed the CNN trunk. \\
Attention and fusion & Eight-head self-attention with dropout 0.1 and residual layer normalization, followed by global mean pooling. Multi-scale pooled CNN features were concatenated through feature-pyramid fusion. \\
Dense head & Two dense blocks of 256 and 128 units with batch normalization, nonlinear activations, and dropout 0.3 and 0.4, followed by a two-logit output layer. \\
Optimization & AdamW with learning rate 0.001 and weight decay 0.01; cosine warm restarts to a minimum learning rate of $10^{-6}$; batch size 8192 before fold-size adjustment; label smoothing 0.05; gradient clipping at 1.0; mixed precision; maximum 100 epochs; early stopping patience 5 with best-state restore. \\
\bottomrule
\end{tabularx}
