We evaluated whether a sparse, low-montage resting-state EEG pipeline could identify clinically interpretable candidate biomarkers of response to transcranial direct current stimulation (tDCS) in adults with treatment-resistant depression under strict patient-level validation. The study used 4-channel eyes-closed EEG and a controlled sweep of 150 successful runs across two model families: an advanced hybrid 1D CNN-LSTM and a linear support vector machine (SVM). The sweep varied window size (2--10 s) and the per-fold feature-selection budget (\texttt{inner-k} 1--70), while holding the consensus feature budget fixed at 10 and enabling both leave-one-participant-out group equalization and SMOTE during training.

The strongest configuration was the hybrid model with 6 s windows and \texttt{inner-k=1}. That run reached patient-level ROC-AUC 0.816, PR-AUC 0.579, balanced accuracy 0.786, accuracy 0.810, and MCC 0.571 over 21 held-out participants. The best SVM configuration (8 s, \texttt{inner-k=30}) reached ROC-AUC 0.510 and MCC 0.277. The hybrid winner was also highly sparse, selecting 1 feature per fold and only 7 unique features overall, with a permutation-tested ROC-AUC advantage over chance ($p=0.008$). Hard-set overlap across folds was modest (mean pairwise Jaccard 0.190; Kuncheva index 0.187). The recurrent features showed perfect mean effect-direction consistency.

These results support a sparse short-timescale EEG framework that recovers a small, interpretable candidate biomarker set while preserving useful patient-level discrimination in a very small cohort. The most recurrent features involved temporal spectral entropy and frontal-temporal asymmetry-derived measures, and their class-conditional selection patterns motivate follow-up validation in larger externally evaluated datasets.
