The strongest patient-level discrimination in this sweep emerged from the sparsest tested configuration. The best hybrid run used \texttt{inner-k=1}, selected only 7 unique recurrent features overall, and exceeded the best linear baseline by a large margin on ROC-AUC and MCC. In this cohort, performance depended on how effectively the model used a small selected subset.

This result fits part of the EEG depression literature and supports a measured interpretation. Prior work has argued that EEG can provide clinically useful baseline markers in major depressive disorder and treatment-response settings, and it has also emphasized the need for tighter biomarker discipline, better standardization, and more realistic expectations about generalization \citep{olbrich2013_eeg,olbrich2015_personalized,leuchter2010_biomarkers,simmatis2023_technical,alonso2017_standardization,Fu2019}. Machine learning studies have likewise reported encouraging treatment-response signals, including combinations of EEG and clinical covariates, yet translation is often limited by data heterogeneity, cohort size, or insufficient interpretability \citep{AlKaysi2017,jaworska2019_leveraging,oakley2022_eeg,shalbaf2018_nonlinear,ebrahimzadeh2021_predicting,zhdanov_svm_prediction,watts2022predicting,cohen2023electroencephalography}.

The present sweep adds a feature-selection view to that literature. The shared feature-selection panels in Figure~\ref{fig:sweep-overview} show that larger feature budgets yield more overlap and many more unique discovered features. Those larger budgets do not improve discrimination. The panels support a small recurring biomarker set with consistent direction of class separation. That reading keeps the modest Jaccard and Kuncheva scores in view and gives appropriate weight to the stronger effect-direction signal. Methodologically, this framing matters because the depression EEG biomarker literature still contains substantial publication bias, limited out-of-sample validation, and known vulnerability to leakage from pre-cross-validation feature processing \citep{Widge2019,Shim2021}. The present pipeline addresses that problem by embedding selection and rebalancing inside participant-level outer folds and then summarizing recurrence and directionality instead of reporting only a single global feature list \citep{Shen2025}.

The same clinical program has also supported other signal representations in recent PSD-based and PLV-based studies, which located informative response-related signal in low-density temporal and frontal-temporal patterns \citep{Moncy2024,Xiao2025PMIP}. In the present sweep, the recurrent feature set again concentrated in TP10-derived and frontal-temporal descriptors. That regional convergence supports the view that the low-montage recordings contain response-relevant information across multiple feature families.

The specific biomarkers in the present sweep are plausible enough to deserve follow-up. \texttt{tp10\_spectral\_entropy} was the most frequently selected feature and skewed toward non-remission-associated folds. Entropy and related nonlinear descriptors have appeared repeatedly in depression EEG studies \citep{Puthankattil2012,Faust2014,Acharya2015}. Pretreatment multiscale entropy and signal-variability measures have also been linked to antidepressant treatment response, although the reported direction depends on temporal scale and recording context \citep{Jaworska2018}. That nuance is important because a recent large resting-state evaluation found complexity metrics to be stable but not to support a simple uniform depression-complexity association \citep{Lord2023}. The present TP10 entropy finding therefore fits a broader complexity literature and supports a credible temporal biomarker signal in this cohort, while still needing external confirmation.

The frontal-temporal beta and gamma difference features also have prior support at the family and regional level. Temporal electrodes, higher-frequency band features, and paired asymmetry terms have been reported as informative in depression EEG studies, and pretreatment frontal-temporal features have been linked to treatment outcome in MDD \citep{Mahato2020,Mumtaz2017}. The current beta and gamma difference terms are therefore better read as family-level extensions of that regional pattern than as exact replications of a previously fixed biomarker.

\texttt{af7\_zero\_crossings} had the clearest remission-skewed selection pattern in the current sweep, but it has less direct precedent as a named biomarker. AF7-centered signal relevance has appeared in adjacent low-montage work \citep{Moncy2025BD}, and broader frontal EEG literature continues to implicate asymmetry and signal-complexity families in depression \citep{Monni2022,Lord2023}. The specific zero-crossing formulation used here is therefore best regarded as a plausible frontal biomarker in this setting and should be tested in independent cohorts. Taken together, the recurrent set emphasized temporal and frontal-temporal descriptors, with limited concentration in any single frontal asymmetry family. This regional profile is compatible with the broader low-montage findings discussed above. The current study contributes a sparse handcrafted biomarker signature with explicit recurrence and effect-direction summaries.

Related home-based tDCS studies in bipolar depression from the same group point in a similar low-montage direction. PSD-based modeling again highlighted AF7 and TP10 signal content, and PLV analyses emphasized frontal-temporal and temporoparietal synchronization patterns \citep{Moncy2025BD,Xiao2025JAD}. These bipolar studies address a different diagnosis and treatment protocol. They support reduced-montage feasibility and signal plausibility in adjacent affective cohorts.

The dataset is relatively small ($n=21$), the confidence intervals are wide, and there is no external validation set. The bottom-row sweep panels describe the selection pipeline itself because the same feature-selection layer feeds both classifiers. Class-conditional ratios also become unstable when a feature is absent from one class, so the manuscript uses deltas and effect direction as the main descriptive summaries. The recurring features can be treated as plausible biomarkers from this cohort that now warrant follow-up validation.

Future work should test whether the same sparse feature set recurs under independent cohorts, alternative low-density montages, and explicit external validation \citep{Dagnino2023}. Adjacent response-prediction work in depression and neuromodulation provides useful targets for that next stage, including EEG-based prediction of antidepressant response, treatment-resistant depression biomarkers, and neuromodulation-specific response signatures \citep{funk2008_prefrontal,bailey2023_concurrent,guo2024_restingstate,romeromarn2026_remotely,kratter2026_stanford,waller2026_transient,sheen2024_response,zeidabadi2025_prediction,reissmann2026_thetacordance,ulrich2025_alterations,pettorruso2024_overcoming}. These extensions should keep stringent patient-level evaluation and sparse interpretable feature budgets in the core study design.
